---
title: "Explore data"
output: html_document
---
## Load data & scripts

```{r, message=FALSE}
setwd('~/Desktop/Prudential')
source("Load.R")
source("ggplot_missing.R")
```

## Look at variables

```{r}
# look at variables
str(train)
```

__What I found:__

* Most variables (`int` columns) are categorical encoded as integers
* A few are numerical like `BMI` and `weight`
* `Product_Info_2` is a string column

## Look at missing data

__Plot missing data__

```{r}
ggplot_missing(train)
```

__These are variables with missing data__

```{r}
countMissingData <- function(column) {
  return (sum(is.na(column)))
}
missing_data <- apply(train[, -1], 2, countMissingData)
missing_data[missing_data > 0]
```

TODO

* Remove them or fill in missing data

__Remove these variables that have lots of missing data:__

```{r}
missing_data[missing_data > 15000]
remove_these <- names(missing_data[missing_data > 15000])
```

__Fill in missing data for these variables:__

```{r}
fill_in_these <- missing_data[missing_data > 0 & missing_data < 15000]
fill_in_these <- names( missing_data[missing_data > 0 & missing_data < 15000] )
apply(train[, fill_in_these], 2, summary)
```
